### 2015-03-02 fundamentals/impl.tex
fixes #94 with the 'just delete it' strategy. I cited the example given in the Simulations section instead

Interchangeability is accomplished by providing inheritable \glspl{API} that define agent-to-agent
interaction and agent-to-environment interaction. For example,
an archetype that inherits the \Class{Region} interface, as in Figure
\ref{fig:agent_uml}, is interchangeable with any other Region agent.
For the archetype developer, this interface provides enormous power
very simply. The \gls{API} abstracts away unnecessary detail while providing
all necessary functionality for interacting with the \Cyclus simulation kernel.

@@

As illustrated in
Figure \ref{fig:simplesim}, the current \Cycamore release provides basic
functionality enabling simple fuel cycle analyses. As future contributions are
vetted, the capabilities in \Cycamore may grow.

\begin{figure}[htbp!]
\begin{center}
\includegraphics{./images/simplesim}
\end{center}
\caption{Material flows through a simple dynamic simulation created with only the simplest \Cycamore archetypes, \Class{Sink} and \Class{Source}.}
\label{fig:simplesim}
\end{figure}

>>>>

Interchangeability is accomplished by providing \glspl{API} that define agent-to-agent
interaction and agent-to-environment interaction, primarily through the
\Class{Agent} and \Class{Trader} interfaces. Figure \ref{fig:agent_uml} shows
the ``inheritance'' structure of the \Class{Agent} class in a \gls{UML} diagram
format. It shows how the \Class{Agent} interface
provides a notion of parent-child hierarchical relationship, where parents can
choose to \textit{deploy} child agents and \textit{decommission} child
agents. For the archetype developer, this interface provides enormous power
very simply. The \gls{API} provides the \Class{Agent} with helpful functionality for
interacting with the \Cyclus simulation kernel while abstracting away unnecessary
detail.

@@

Section \ref{sec:simulations} will demonstrate how the current \Cycamore
release provides basic functionality enabling simple fuel cycle analyses. As
future contributions are vetted, the capabilities in \Cycamore may grow.
